%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Analyst} % Job title
    {Wellcome Trust} % Organization
    {Manchester, UK} % Location
    {May 2020 - September 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integrated and analysed more tha 140,000 data from Wellcome Global Monitor (WGM) 2018, UNICEF, and UN to develop a holistic view of current global vaccine attitudes with aims to support the policymakers in devising effective immunisation scheme to deal with COVID-19.}
        \item {Introduced a novel approach to the research of vaccine attitudes through the implementation of robust data mining framework and advanced analytical techniques including visual-driven data exploration, clustering and machine learning algorithms.}
        \item {Successfully determined new factors associated with vaccine attitudes through well-built decision tree, random forest, and gradient boosting models with significantly high accuracy score of up to 90\%.}
        \item {Identified high risk country clusters with low vaccine attitudes or coverage using k-mean clustering algorithms and proposed feasible solutions to enhance the adoption rate of COVID-19 vaccine.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Performance Specialist} % Job title
    {Gapture Malaysia Sdn Bhd} % Organization
    {Kuala Lumpur, MY} % Location
    {Aug 2018 - Aug 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented an accumulated budgets of RM300,000 Google and Facebook ads campaign, generating over 4,000 leads and 90,000 clicks for all campaigns.}
        \item {Transformed the optimisation flow of Google search ads through development of automated negative keywords screening process which helps reduced original process time by 50\%.}
        \item {Integrated analytics tools which has successfully tracked over 1,000 events and increased conversion rate by 5\%.}
        \item {}
        \item {Build automated reporting pipeline Prepared monthly report using data mining and data visualization software to build effective feedback system and relationships with clients.}
        \item {Created and managed Facebook contents for a global oil \& gas company, gaining over 500 organic page likes within 6 months.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Marketing Intern} % Job title
    {The Inside Scoop Sdn Bhd} % Organization
    {Kuala Lumpur, MY} % Location
    {Feb 2018 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planned and executed 4 high-yielding marketing campaigns, e.g. generated more than 50 cake orders with an estimated total revenue of RM6,000 for Mother’s Day campaign.}
        \item {Negotiated with local and China suppliers and helped company saved 37\% of buying cost. }
        \item {Liaised with accounting department to resolve international transaction issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Marketing Intern} % Job title
    {AirAsia Bhd} % Organization
    {Kuala Lumpur, MY} % Location
    {May 2016 - Jun 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed weekly promotional contents on AirAsia’s website and email for Australia and New Zealand market.}
        \item {Conducted a rigorous competitor analysis on 5 different airlines along with other market researches to explore new market opportunities in Sharjah and Medina.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
