%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvprojects}

%---------------------------------------------------------
  \cvproject
    {} % Affiliation/role
    {Dissertation: Evaluating Global Vaccine Attitudes Using Data Mining Approach} % Organization/group
    {Manchester, UK} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {An in-depth study on global vaccine attitudes and coverage aimed to assist policymakers in devising effective immunization scheme to cope with COVID-19.}
        \item {The research was performed through a robust data mining approach that involves data preprocessing, exploratory data analysis, clustering analysis, and predictive modeling.}
        \item {Machine learning algorithms implemented comprised of k-means, decision tree, random forest, and gradient boosting.}
        \item {Tools and packages used include Python, R, Numpy, Pandas, Scikit-Learn, MICE, Seaborn, Matplotlib, ggplot2, Tableau, and etc.}
      \end{cvitems}
    }

  \cvproject
    {} % Affiliation/role
    {Sales Forecast for Drug Store} % Organization/group
    {Manchester, UK} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Forecasted sales for a large drug store chain in Europe from a dataset consisting of 1M+ sales records and other data such as promotion through time series analysis and random forest.}
        \item {Data preprocessing was conducted on R using MICE package.}
        \item  {Exploratory data analysis and predictive modelling were performed through Python with Scikit-Learn, Facebook Prophet, Seaborn, and etc.}
      \end{cvitems}
    }

  \cvproject
    {} % Affiliation/role
    {Simulation Modelling for Massachusetts General Hospital's PATA} % Organization/group
    {Manchester, UK} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Simulated patient in-and-out flows with the application of Queuing Theory and proposed solution to resolve bottleneck issues in the hospital through SIMUL8.}
      \end{cvitems}
    }

  \cvproject
    {} % Affiliation/role
    {Performance \& Efficiency Analysis for Fashion Retailer's Suppliers} % Organization/group
    {Manchester, UK} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Ranked the best supplier according to their attributes through multiple-criteria decision analysis, multiple objective linear programming, and data envelopment analysis.}
        \item {Performed analysis using IDS and Excel Solver.}
      \end{cvitems}
    }

  \cvproject
    {} % Affiliation/role
    {Travelling Santa Problem} % Organization/group
    {Manchester, UK} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Optimized Santa's delivery route by minimizing reindeer weariness using random search and simulated annealing algorithms
        that were applied on 100K dataset consisting of gifts information such as latitude and longitude.}
        \item {Conducted on Python using packages including Scikit-learn, SciPy, Matploblib, Seaborn, and etc.}
      \end{cvitems}
    }

  \cvproject
    {} % Affiliation/role
    {Jelly Bean Sales Regression Analysis} % Organization/group
    {Manchester, UK} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Built a marketing mix model via linear regression model in R to find the association between jelly bean sales and promotion mix.}
        \item {Implemented k-fold cross validation and assumption tests to enhance model robustness.}
      \end{cvitems}
    }

  \cvproject
    {} % Affiliation/role
    {Optimization of Student-Project Allocation} % Organization/group
    {Manchester, UK} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Optimize the allocation of student to research supervisor through the application of linear programming technique
        including objective and constraints formulation, and solve the problem using Excel Solver.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cvprojects}
